Review of Edge Detectors

### 2014-05-26 edge-detection-review-2nd-revision-v2.tex
changed url of demo

%-------------------------------------------------------------------------------
% A Review of Classic Edge Detectors - v10
% by Haldo Spontón & Juan Cardelino
% IPOL 2012
%-------------------------------------------------------------------------------

\documentclass{ipol}
\ipolSetYear{2012}
\ipolSetMonth{06}
\ipolSetDay{06}
%\ipolSetID{arced}
\ipolSetTitle{A Review of Classic Edge Detectors}
\ipolSetAuthors{Haldo Spont\'on$^1$, Juan Cardelino$^2$}
\ipolSetAffiliations{%
$^1$ IIE, UdelaR, Uruguay (\texttt{haldos@fing.edu.uy})\\
$^2$ IIE, UdelaR, Uruguay (\texttt{juanc@fing.edu.uy})}

@@

\begin{ipolCode}
For all the algorithms reviewed, an open source C implementation is provided that can be downloaded from 
the IPOL publication of this article. An 
\href{http://dev.ipol.im/~haldos/ipol_demo/xxx_edges/}{online demonstration}\footnote{\url{http://dev.ipol.im/~haldos/ipol_demo/xxx_edges/}} is also available, where 
you can test and reproduce our results.
\end{ipolCode}

>>>>

%-------------------------------------------------------------------------------
% A Review of Classic Edge Detectors - v10
% by Haldo Spontón & Juan Cardelino
% IPOL 2014
%-------------------------------------------------------------------------------

\documentclass{ipol}
\ipolSetYear{2014}
\ipolSetMonth{05}
\ipolSetDay{26}
%\ipolSetID{arced}
\ipolSetTitle{A Review of Classic Edge Detectors}
\ipolSetAuthors{Haldo Spont\'on$^1$, Juan Cardelino$^2$}
\ipolSetAffiliations{%
$^1$ IIE, UdelaR, Uruguay (\texttt{haldos@fing.edu.uy})\\
$^2$ IIE, UdelaR, Uruguay (\texttt{juanc@fing.edu.uy})}

@@

\begin{ipolCode}
For all the algorithms reviewed, an open source C implementation is provided that can be downloaded from 
the IPOL publication of this article. An 
\href{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/}{online demonstration}\footnote{\url{http://dev.ipol.im/~juanc/ipol_demo/sc_edges/}} is also available, where 
you can test and reproduce our results.
\end{ipolCode}
